Derive final annotations based on NBAtlas reference

### 2025-08-25 analyses/cell-type-neuroblastoma-04/final-annotation.Rmd
remove unneeded stuff

1. If `SingleR` and `scANVI/scArches` labels exactly agree, we assign that label
2. If broad label families (e.g., `T cell` would be the broad family for `CD4+ T cell`) for `SingleR` and `scANVI/scArches` labels agree, we assign the broad family label.
    * See [`references/nbatlas-label-map.tsv`](references/nbatlas-label-map.tsv) and [`references/README.md`](references/README.md) for how labels were mapped to families.
3. If `SingleR` and `scANVI/scArches` labels disagree, we then compare to the consensus cell type; if at least one inference agrees with the consensus cell type, we assign the inferred label.
    * We perform this first at the label level and then at the broad family level.
4. If the consensus cell type is `Unknown` and one of `SingleR` or `scANVI/scArches` labels is `Neuroendocrine` and the other label is one of `Schwann cell`, `Stromal other` or `fibroblast`, we assign the `Neuroendocrine` label
5. Finally, following the conclusions of Bonine et al. (2024), we designate any cell labeled as `Neuroendocrine` as a tumor cell.

@@

# pull out NE ontology for assignment code
ne_ontology <- ontology_slim_df$CL_ontology_id[ontology_slim_df$NBAtlas_label == "Neuroendocrine"]

>>>>

1. If `SingleR` and `scANVI/scArches` labels exactly agree, we assign that label
2. If broad label families (e.g., `T cell` would be the broad family for `CD4+ T cell`) for `SingleR` and `scANVI/scArches` labels agree, we assign the broad family label.
    * See [`references/nbatlas-label-map.tsv`](references/nbatlas-label-map.tsv) and [`references/README.md`](references/README.md) for how labels were mapped to families.
3. If `SingleR` and `scANVI/scArches` labels disagree, we then compare to the consensus cell type; if at least one inference agrees with the consensus cell type, we assign the inferred label.
    * We perform this first at the label level and then at the broad family level.
4. If the consensus cell type is `Unknown` and one of `SingleR` or `scANVI/scArches` labels is `Neuroendocrine` and the other label is one of `Schwann`, `Stromal other` or `Fibroblast`, we assign the `Neuroendocrine` label
5. Finally, following the conclusions of Bonine et al. (2024), we designate any cell labeled as `Neuroendocrine` as a tumor cell.

@@
